---
title: "AtacAnnoR “Combine and Discard” strategy"
output: html_document
date: "2023-03-06"
author: "Lejin Tian"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


We develop a “Combine and Discard” strategy to improve the accuracy of query cell annotations given multiple references. The cost is discarding some cells with inconsistent labels across different references' annotation results. 


----

## Load required packages and datasets

```{r, echo = T}
library(AtacAnnoR)
setwd('~/txmdata/scATAC_seq/AtacAnnoR')
SeuratObj_ATAC <- readRDS('./data/10X-Multiome/SeuratObj/SeuratObj_ATAC.RDS')
AtacAnnoR_pred_list <- readRDS('./data/tools_pred/AtacAnnoR_pred_list.RDS')
```


----

## Construct a prediction data frame

Each row represents a query cell and each column represents the labels predicted by a specific reference.

```{r, echo = T}
pred_df <- data.frame(Hao = AtacAnnoR_pred_list$Hao,
                      Stephenson = AtacAnnoR_pred_list$Stephenson,
                      Wilk = AtacAnnoR_pred_list$Wilk,
                      Zhu = AtacAnnoR_pred_list$Zhu,
                      Monaco = AtacAnnoR_pred_list$Monaco)
head(pred_df)
```





## Run “Combine and Discard” strategy based on each reference


```{r, echo = T}
merged_laels <- get_merged_labels(pred_df)
datasets <- c('Hao','Stephenson','Wilk','Zhu','Monaco')
for(dataset in datasets){
  print(paste0('======================== ',dataset,' ========================'))
  GML <- AtacAnnoR:::GET_GML(dataset)
  REF <- switch(dataset,
                'Hao' = 1,
                'Stephenson' = 2,
                'Wilk' = 3,
                'Zhu' = 4,
                'Monaco' = 5) 
  discarded_idx <- Combine_and_Discard(merged_laels,reference = REF,fraction = 0.05,verbose = T)
  before_bench <- get_benchmark(GML(SeuratObj_ATAC$true),GML(pred_df[[dataset]]))
  after_bench <- get_benchmark(GML(SeuratObj_ATAC$true[-discarded_idx]),GML(pred_df[[dataset]][-discarded_idx]))
  print('Before benchmark:')
  print(before_bench)
  print('After benchmark:')
  print(after_bench)
}
```

The results show that the accuracies are improved and the number of discarded cells is ~1,000. The left cells are enough for downstream analyses.

----

## Session Info

```{r, echo = T}
sessionInfo()
```





